Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-08-17 writeup/rocha_etal.tex
Edits acknowledgements

\section{Statistics of the surface lateral velocity gradient tensor}
To study the seasonality in the surface velocity, we calculate the lateral velocity gradient tensor
\begin{equation}
\left[\begin{matrix} u_x & u_y\\ v_x&v_y \end{matrix}\right]
\end{equation}
using a centered
second-order finite difference scheme. We then diagnose
the vertical vorticity
\begin{equation}
\zeta \equiv v_x - u_y\, ,
\end{equation}
lateral rate of strain
\begin{equation}
  \alpha \equiv [(u_x-v_y)^2 + (u_y + v_x)^2]^{1/2}\,,\\
\end{equation}
and horizontal divergence
\begin{equation}
\delta \equiv u_x + v_y\, .
\end{equation}
These diagnostics highlight the submesoscale structures in the flow
\citep[e.g.,][]{capet_etal2008a,shcherbina_etal2013}.

@@

\section{Seasonality of submesoscale dynamics}
The results of figure \ref{fig2}a-c show that submesoscale surface
 variability stems from different dynamics in summer than in winter.
 To characterize these differences, we calculate
joint probability distributions (joint-PDF) of
vorticity-strain and vorticity-Laplacian of sea-surface height (Figure \ref{fig3}).

@@

@@

\begin{acknowledgments}
 William R. Young and the referees --- Christian Buckingham and two anonymous ---
  provided constructive and helpful comments. Greg Wagner first
 suggested that the near-surface shape of the baroclinic modes may change seasonally.
 We thank the MITgcm community and our colleagues at the NASA Advanced
Supercomputing (NAS) Division for their awesome support.
This research was funded by NSF (OCE1357047) and NASA (NNX13AE44G,NNX13AE85G,NNX16AH67G).
The LLC output can be obtained from the ECCO project (\texttt{http://ecco2.org/llc$\_$hires}). The altimeter products were produced by Ssalto/Duacs
and distributed by AVISO, with support from CNES (\texttt{http://www.aviso.altimetry.fr/duacs/}).
Codes and output files are available online at the project repository
 (\texttt{https://github.com/crocha700/UpperOceanSeasonality}).
\end{acknowledgments}

>>>>

\section{Bulk statistics of the surface lateral velocity gradient tensor}
To study the seasonality in the surface velocity, we calculate the lateral velocity gradient tensor
\begin{equation}
\left[\begin{matrix} u_x & u_y\\ v_x&v_y \end{matrix}\right]
\end{equation}
using a centered
second-order finite difference scheme. We then diagnose
the vertical vorticity
\begin{equation}
\zeta \equiv v_x - u_y\, ,
\end{equation}
lateral rate of strain
\begin{equation}
  \alpha \equiv [(u_x-v_y)^2 + (u_y + v_x)^2]^{1/2}\,,\\
\end{equation}
and horizontal divergence
\begin{equation}
\delta \equiv u_x + v_y\, .
\end{equation}
These diagnostics highlight the submesoscale structures in the flow
\citep[e.g.,][]{capet_etal2008a,shcherbina_etal2013}.

@@

\section{Joint probability density functions}

The results of figure \ref{fig2}a-c show that submesoscale surface
 variability stems from different dynamics in summer than in winter.
 To characterize these differences, we calculate
joint probability distributions (joint-PDF) of
vorticity-strain and vorticity-Laplacian of sea-surface height (Figure \ref{fig3}).

@@

\section{Wavenumber-frequency spectrum}

@@

\begin{acknowledgments}
 William R. Young and the reviewers --- Christian Buckingham and two anonymous referees ---
  provided exceptionally helpful and constructive comments. Greg Wagner first
 suggested that the near-surface shape of the baroclinic modes may change seasonally.
 We thank the MITgcm community and our colleagues at the NASA Advanced
Supercomputing (NAS) Division for their awesome support.
This research was funded by NSF (OCE1357047) and NASA (NNX13AE44G,NNX13AE85G,NNX16AH67G).
The LLC output can be obtained from the ECCO project (\texttt{http://ecco2.org/llc$\_$hires}). The altimeter products were produced by Ssalto/Duacs
and distributed by AVISO, with support from CNES (\texttt{http://www.aviso.altimetry.fr/duacs/}).
Codes and output files are available online at the project repository
 (\texttt{https://github.com/crocha700/UpperOceanSeasonality}).
\end{acknowledgments}
